\chapter{Introduction}

This board allows to connect FPix modules using a flex cable to connect it to the DTB.

The following conventions are used throughout this document:
\begin{itemize}
    \item SCSI-connector: this refers to the 68-pin connector, which will be used to connect the adapter to the DTB.
    \item SMK-connector: this is a 2$\times$20 pin connector to connect to the FPix module using standard FPix flex cables.
    \item GND: ground.
    \item HV: High voltage, routed through the DTB and supplied by an external power supply.
    \item VA: Supply voltage for analog circuits in the ROC.
    \item VD: Supply voltage for digital circuits in the TBM and ROC.
    \item 3V3: 3.3\,V supply for support circuits.
\end{itemize}

\chapter{Design considerations}
The board has been designed as a 4-layer PCB with the following topology:
\begin{center}
\begin{tabular}{cc}
	\toprule %-------------------------------------------------------------------------------------------------
Layer & Description \\
	\midrule %-------------------------------------------------------------------------------------------------
Top & Main signal layer \\
2nd & GND plane \\
3rd & Power plane, distributed $VA$, $VD$, and $HV$
	\bottomrule %-------------------------------------------------------------------------------------------------
\end{tabular}
\end{center}

\section{Signal routing}

\section{Impedance matching of TBM signals}

\section{RTD bridge}

\section{Form factor}

\section{HV protection}
High voltage is supplied via the DTB\footnote{The DTB has a relay to control HV from a HV power supply and passes it via a 100\,k$\Omega$ resistor to the SCSI cable. See the DTB documentation about its HV safety.}. The following measures have been taken:
\begin{itemize}
    \item The HV is routed entirely in an inner layer.
    \item There are some spots on the board where a HV is exposed:
    \begin{enumerate}
	\item HV pin at the SCSI connector (pin 68). Accessible on the back of the board.
	\item Two vias around the SMK connector
    \end{enumerate}
\end{itemize}

